---
title: "WeeViewImageFormat"
author: "Chris Rooper"
date: "5/27/2020"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Format 3d images

This is code to take the images from a weeview 3d camera, crop them and format them for use in Sebastes stereo-image analysis software.



To install the package use the lines below. The function requires the "RSQLite" and "magick" packages that can be downloaded and installed from the CRAN repository.

```{r install library, eval=FALSE}

devtools::install_github("rooperc4/WeeViewImageFormat")
library(WeeViewImageFormat)

```


The package has a single function that can be run using the following code. The function prompts the user to point to a folder where the Weeview photos are located that need to be converted. Then it will print the list of images in that folder. Next it will prompt the user for a location to place the converted images and the metadata required by Sebastes. It will then do the image conversion and produce the required metadata. It is important to note that the metadata generated by this function is not informative about the images. The function can also be run from the command line using the second example where the from and to file folders are specified. There is limited help documentation as well. 

```{r run function, eval=FALSE}
#Example 1: User is prompted for file locations
ImageFormat()

#Example 2: Command line specification of file locations
ImageFormat("D:/Weeview/PHOTO","C:/Users/rooperc/Desktop/WeeviewTest")
```



